### 2021-10-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c3958339ff323180e7e2ff4617d752100d74ac9f 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@6c9053330422f4b3622416e17c37af0e447b7b55 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@bbdcc5611f22bf276b9d7a4ea2878d6145bf92b9 🚀

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

@@

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

@@

Forecasting in ecology.

Forecasting in weather, introduce computers.

@@

Transition to theme of optimization given unknown information. In face
of uncertainty, decision making is an optimization problem.

@@

@@

>>>>

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Thesis proposal}
\vskip 5em

@@

\vfill
The proposal for my thesis, \emph{Simulation models for predictive
ecology}

@@

Forecasting in ecology. Forecasting in weather, introduce computers.

@@

Transition to theme of optimization given unknown information. In face
of uncertainty, decision making is an optimization problem. Frame
optimization problem mathematically an introduce concept of
solution-space and constraint.

Transition to how this is applied in ecology. Introduce idea of
monitoring network. Transition to specifics of this thesis.

\begin{figure}
\centering
\includegraphics{./figures/thesisconcept.png}
\caption{thesis concept}
\end{figure}

@@

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

@@

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

### 2021-10-05 preprint.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c3958339ff323180e7e2ff4617d752100d74ac9f 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@6c9053330422f4b3622416e17c37af0e447b7b55 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@bbdcc5611f22bf276b9d7a4ea2878d6145bf92b9 🚀

\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
manuscripts using markdown and github actions}}}

@@

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

>>>>

\noindent {\LARGE \textbf{\textsf{Thesis proposal}}}

@@

The proposal for my thesis, \emph{Simulation models for predictive
ecology}
